---
title: "BMI_Covid"
author: "Alish Palmos"
date: "18/10/2021"
output: html_document
---

This is sensitivity analyes between BMI and our significantly associated markers. 

```{r echo=FALSE}
rm(list=ls())
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

setwd("/scratch/groups/ukbiobank/usr/alish/Covid19/MR/")
```

```{r include=FALSE}
library(data.table)
library(jtools)
library(knitr)
library(broom)
library(sandwich)
library(tidyverse)
library(ggplot2)
library(sgof)
library(TwoSampleMR)
library(qvalue)
library(kableExtra)
```

#Read in GSMR data
#BMI exposure 

```{r echo=FALSE}

#BMI

setwd("/scratch/groups/ukbiobank/usr/alish/Covid19/MR/BMI/output/")

bmi_mr <- list.files(pattern = "*.e8.gsmr")

bmi_mr = lapply(bmi_mr, read.delim)

bmi_mr <- do.call(rbind.data.frame, bmi_mr)

bmi_mr <- bmi_mr %>%
  filter(nsnp >= 1)

bmi_n <- count(bmi_mr)
```

#Make sure we have BMI as exposure
```{r}
mr_df <- bmi_mr

mr_df <- mr_df[!grepl("BMI", mr_df$Outcome),]
```

# Combine full data, work out odds ratios and 95% CI
```{r}

mr_df_all  <-  mr_df

mr_df_all$Beta_exponent <- exp(mr_df_all$bxy)
mr_df_all$LCI <- mr_df_all$Beta_exponent - (mr_df_all$se * 1.96)
mr_df_all$UCI <- mr_df_all$Beta_exponent + (mr_df_all$se * 1.96)

mr_df_all$Exposure <- gsub(".txt", "",mr_df_all$Exposure)
mr_df_all$Outcome <- gsub(".txt", "",mr_df_all$Outcome)
```

# Compute q-values and add them to the large combined data frame
```{r}
pvalues <- mr_df_all$p

qobj <- qvalue(p = pvalues)

lfdr <- qobj$lfdr
summary(pvalues)
hist(pvalues)
plot(qobj)

qvalues <- as.matrix(pvalues)
mr_df_all$qvalue <- cbind(pvalues)
```


# Adjusted p-values using SGoF method
```{r}
p <- SGoF(mr_df_all$p)
summary(p)

plot(p)
```

# Adjusted p-values to be inclued in the data frame & sorted by p-value
```{r}
mr_df_all$p.adjust <- p.adjust(p = mr_df_all$p, method = "fdr")

mr_df_all <- mr_df_all[order(mr_df_all$Exposure, +abs(mr_df_all$p) ), ]

sorted <- mr_df_all[order(mr_df_all$p),]

head(sorted, n = 15)

kable(sorted)
```

#BMI outcome 

```{r echo=FALSE}

#BMI

setwd("/scratch/groups/ukbiobank/usr/alish/Covid19/MR/BMI/output/")

bmi_mr <- list.files(pattern = "*.e6.gsmr")

bmi_mr = lapply(bmi_mr, read.delim)

bmi_mr <- do.call(rbind.data.frame, bmi_mr)

bmi_mr <- bmi_mr %>%
  filter(nsnp >= 1)

bmi_n <- count(bmi_mr)
```

#Make sure we have BMI as outcome

```{r}
mr_df <- bmi_mr

mr_df <- mr_df[!grepl("BMI", mr_df$Exposure),]
```

# Combine full data, work out odds ratios and 95% CI
```{r}

mr_df_all  <-  mr_df

mr_df_all$Beta_exponent <- exp(mr_df_all$bxy)
mr_df_all$LCI <- mr_df_all$Beta_exponent - (mr_df_all$se * 1.96)
mr_df_all$UCI <- mr_df_all$Beta_exponent + (mr_df_all$se * 1.96)

mr_df_all$Exposure <- gsub(".txt", "",mr_df_all$Exposure)
mr_df_all$Outcome <- gsub(".txt", "",mr_df_all$Outcome)
```

# compute q-values and add them to the large combined data frame
```{r}
pvalues <- mr_df_all$p
qobj <- qvalue(p = pvalues)
lfdr <- qobj$lfdr
summary(qobj)
hist(qobj)
plot(qobj)

qvalues <- as.matrix(qobj$qvalues)
mr_df_all$qvalue <- cbind(qvalues)
```

# Adjusted p-values using SGoF method
```{r}
p <- SGoF(mr_df_all$p)
summary(p)

plot(p)
```

# Adjusted p-values to be inclued in the data frame & sorted by p-value
```{r}
mr_df_all$p.adjust <- p.adjust(p = mr_df_all$p, method = "fdr")

mr_df_all <- mr_df_all[order(mr_df_all$Exposure, +abs(mr_df_all$p) ), ]

sorted <- mr_df_all[order(mr_df_all$p),]

head(sorted, n = 15)

kable(sorted)
```
